---
title: "Practical 8 - Risk Models I"
date: "22/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#disable scientific notation 
options(scipen=999)

#automatically open/install packages
packages <- c("readxl", "knitr")

package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE)
    library(x, character.only = TRUE)
  }
})
```

---

#  Question 1

---

Consider the four equations shown in Figures A - D. As revision for LaTeX, your task in this question is to reproduce each of these equations and store them as you would in a practical test. The first one will be provided as an example.

Some tips/notes:

* Don't know the specific function to use? A quick Google search will almost always give you what you need.

* All backslashes must appear in *pairs*, otherwise you will not be able to store your answer.

The first equation is

$$\frac{d^3}{dt^3}\log M_S(t) = \lambda\left[\frac{d^3}{dt^3}M_X(t) - 1\right]_{t=0} = \lambda m_3$$

$$
M(t)=\int_{0}^{\infty}e^{tX}f(x)dx

$$

```{r Question1, echo = FALSE}

# how to actually save the answer
Q1 <- "\\frac{d^3}{dt^3}\\log M_S(t) = \\lambda\\left[\\frac{d^3}{dt^3}M_X(t) - 1\\right]_{t=0} = \\lambda m_3"

Q1 <- "M(t)=\\int_{0}^{\\infty}e^{tX}f(x)dx
"
```



---

#  Question 2

---

Consider the three kinds of policies described below. For each policy, simulate 10 000 random observations and calculate the following for the aggregate claims paid $S$:

* Mean

* Variance

* Coefficient of skewness

* Probability of exceeding R 1 000 000

The three policies are as follows:

1. Individual claim amounts on a group policy are uniformly distributed over the interval $[10000,35000]$. The probability of a claim on such a policy is 45%. The maximum number of claims on such a policy is 100.

2. Individual claim amounts follow a $Gamma$ distribution with $\alpha = 2000$ and $\beta = 0.2$. There is no limit to the number of claims that can be made on this policy within a year, however the average number of claims is known to be 100. The variance of the claim number is also thought to be 100.

3. A high-risk policy covering a total of 200 lives with a probability of claiming equal to 50%. Individual claim amounts follow an exponential distribution with $\theta = 0.0001$.

Use a seed value of 23 for each simulation (i.e. reset the seed before simulating the number of claims for each policy). An Excel file called "**Practical_8_Data.xlsx**" is included with the same parameter information given above. Your script should be able to import the values from this file and utilize them in the simulation in an adaptive way in a test.

---

## Answer

```{r Question2, echo = FALSE}


#Adaptive version


library("readxl")
Data<-read_xlsx("Practical_8_Data.xlsx")
Results<-matrix(0,nrow=nrow(Data),ncol=4)
n_sim<-10000



S_sim<-function(claim_dist,claim_params,n){
  #initialise empty S vector
  s<-length(n)
  #simulate claim numbers and calculate S
  if(claim_dist=="uniform"){
    for(j in 1:length(n)){
      x<-runif(n[j],min=claim_params[1],max=claim_params[2])
      s[j]<-sum(x)
    }
  }else if(claim_dist=="normal"){
    for(j in 1:length(n)){
      x<-rnorm(n[j],mean=claim_params[1],sd=claim_params[2])
      s[j]<-sum(x)
      
    }
  }else if(claim_dist=="gamma"){
    for(j in 1:length(n)){
      x<-rgamma(n[j],shape=claim_params[1],rate=claim_params[2])
      s[j]<-sum(x)
  }
    
  }else if(claim_dist=="exponential"){
    for(j in 1:length(n)){
      x<-rexp(n[j],rate=claim_params[1])
      s[j]<-sum(x)
    }
  }else if(claim_dist=="pareto"){
    for(j in 1:length(n)){
      x<-rPareto(n[j],t=claim_params[1],alpha=claim_params[2])
      s[j]<-sum(x)
    }
    
  }else if(claim_dist=="log-normal"){
    for(j in 1:length(n)){
      x<-rlnorm(n[j],meanlog=claim_params[1],sdlog=claim_params[2] )
      s[j]<-sum(x)
    
    }
  }
  return(s)
}



Results <- matrix(0, nrow = 4, ncol =  3)
n_sim <- 10000

for (i in 1:nrow(Data)) {
  set.seed(23)
  
  if(!(is.na(Data$`Max number of claims`[i]))){
    #if there is a maximum we use a binomial
    n <- rbinom(n_sim,Data$`Max number of claims`[i],Data$`Probability of claim`[i])
  }else{
    n <- rpois(n_sim,Data$`Mean number claims`[i])
}

s <- S_sim(Data$`Claim distribution`[i],
           unlist(Data[i,c(7:ncol(Data))]),
           n)

Results[i,1] <- mean(s)
Results[i,2] <- sd(s)
skewness <- sum((s - mean(s))^3)/length(s)
Results[i,3] <- skewness/var(s)^(3/2)
Results[i,4] <- length(s[s > 1000000])/length(s)
}

Results <- round(as.data.frame(Results),3)
rownames(Results) <- paste("Policy",c(1:nrow(Data)),sep = "")
colnames(Results) <- c("Mean","Variance","Coeff_Skew","P(X > 1 mill)")
```

---

# Question 3

---

Consider Subsection 3.7 in the notes. The objective of this question is to write a function that will calculate the minimum number of policies sold ($n$) to guarantee with a desired level of certainty that an insurance company will turn a profit.

The distributions chosen for the claims, expenses and number of claims as well as their parameter values should be function arguments (i.e. they must be variables and not hardcoded).

Your function should consider the following (i.e. receive this information as input):

* The annual premium on an insurance policy.

* The distribution for the number of claims $N$ and its parameter values.

* The distribution for individual claims $\{X_i\}$ and its parameter values.

* The distribution for expenses on claims $\{Y_i\}$ and its parameter values.

* The percentage of certainty desired in the estimate.

Some tips:

* I answered this question using three functions (one function to set up the moments for the claim and expense distributions, another to set up the moments for the number of claims and the last function to actually use the moments to calculate $n$).

* My final function had a total of 8 parameters (the distribution name and parameters for the claims, expenses and number of claims respectively, the premium and the % of certainty).

* You may assume that $S$ has an approximately normal distribution.

* Independence is as established in the notes.

* There is always more than one way to achieve the same result in $\mathtt{R}$, if you set up your function(s) differently that is perfectly fine as long as it produces the correct final answer and does so in an adaptive manner.

---

## Answer:

```{r Question3, echo=FALSE}

X_dist <- function(claim_dist, claim_params){
  if (claim_dist == "uniform"){
    EX <- (1/2)*(claim_params$a + claim_params$b)
    VarX <- (1/12)*(claim_params$b - claim_params$a)**2
    EX2 <- VarX + EX**2
  } else if (claim_dist == "gamma"){
    EX <- claim_params$alpha/claim_params$beta
    VarX <- claim_params$alpha/(claim_params$beta)**2
    EX2 <- VarX + EX**2
  } else if (claim_dist == "normal"){
    EX <- claim_params$mu
    VarX <- claim_params$sigma**2
    EX2 <- VarX + EX**2
  } else if(claim_dist=="pareto"){
    EX<-claim_params$lambda/(claim_params$alpha-1)
    VarX<-((claim_params$alpha)*(claim_params$lambda**2))/(((claim_params$alpha-1)**2)*(claim_params$alpha-2))
    EX2<-VarX+EX**2
    
    
  }else if(claim_dist=="log-normal"){
    EX<-exp(claim_params$mu+(1/2)*claim_params$sigma**2)
    VarX<-exp(2*claim_params$mu+claim_params$sigma**2)*(exp(claim_params$sigma**2)-1)
    EX2<-VarX+EX**2
  }#add weibull distr.
 
  claim_moments <- list(EX, VarX, EX2)
  names(claim_moments) <- c("E[X]", "Var(X)", "E[X2]")
  return(claim_moments)
}

N_dist <- function(size_dist, size_params){
  if (size_dist == "poisson"){
    EX <- size_params$lambda
    VarX <- size_params$lambda
  } else if (size_dist == "binomial"){
    EX <- size_params$prob
    VarX <- size_params$prob(1-size_params$prob)
  }
 
  size_moments <- list(EX, VarX, size_dist)
  names(size_moments) <- c("E[X]", "Var(X)", "Distribution")
  return(size_moments)
}

min_n <- function(claim_dist, claim_params, size_dist, size_params, expense_dist, expense_params, premium, perc){
  X_moments <- X_dist(claim_dist, claim_params)
  Y_moments <- X_dist(expense_dist, expense_params)
  N_moments <- N_dist(size_dist, size_params)
 
  E_S_coef <- N_moments$`E[X]`*(X_moments$`E[X]` + Y_moments$`E[X]`)
  Var_S_coef <- N_moments$`E[X]`*(X_moments$`Var(X)` + Y_moments$`Var(X)`) +
                N_moments$`Var(X)`*(X_moments$`E[X]` + Y_moments$`E[X]`)**2
 
  n <- ceiling((qnorm(perc)*(sqrt(Var_S_coef))/(premium - E_S_coef))**2)
  return(n)
}

Q3_ans <- min_n(claim_dist = "pareto",
                claim_params = list(lambda = 0.1, alpha = 0.2),
                size_dist = "poisson",
                size_params = list(lambda = 0.4),
                expense_dist = "log-normal",
                expense_params = list(mu = 0.2, sigma = 0.5),
                premium = 80,
                perc = 0.99)

print(paste("The minimum number of policies that need to be sold is ", Q3_ans, ".", sep = ""))

```


